Using IRS Data to Predict Electric Vehicle Count

### 2024-08-06 products/manuscript/Manuscript.qmd
add citations to manuscript

## Introduction
The increasing adoption of electric vehicles (EVs) is a pivotal shift in the transportation sector, driven by growing environmental concerns, advancements in technology, and supportive government policies. Understanding the factors that influence the distribution of EVs is essential for developing targeted policies and infrastructure, such as charging stations and incentives. However, EV adoption is not uniform across regions; it varies significantly based on socio-economic and demographic factors. This study aims to explore these variations by predicting vehicle counts, particularly EVs, at the zip code level using a comprehensive dataset that combines electric vehicle registration data with individual income tax statistics from the Internal Revenue Service (IRS).

@@

{{< pagebreak >}}
## Citations
Jain, A. (n.d.). Electric vehicle population [Data set]. Kaggle. Retrieved June 6, 2024, from https://www.kaggle.com/datasets/jainaru/electric-vehicle-population <br/><br/>

>>>>

## Introduction
The increasing adoption of electric vehicles (EVs) is a pivotal shift in the transportation sector, driven by growing environmental concerns, advancements in technology, and supportive government policies. Understanding the factors that influence the distribution of EVs is essential for developing targeted policies and infrastructure, such as charging stations and incentives. However, EV adoption is not uniform across regions; it varies significantly based on socio-economic and demographic factors. This study aims to explore these variations by predicting vehicle counts, particularly EVs, at the zip code level using a comprehensive dataset that combines electric vehicle registration data @kaggle with individual income tax statistics from the Internal Revenue Service (IRS) @irs.

@@

{{< pagebreak >}}
## Citations
Jain, A. (n.d.). Electric vehicle population [Data set]. Kaggle. Retrieved June 6, 2024, from https://www.kaggle.com/datasets/jainaru/electric-vehicle-population <br/>
